---
name: Mitchell O'Hara-Wild
date: "`r format(Sys.time(), '%B, %Y')`"
qualifications: BCom(Hons), BSc
position: Data Scientist
address: 58 Madeleine Rd, Clayton
phone: +61 408 259 421
email: mail@mitchelloharawild.com
website: mitchelloharawild.com
github: mitchelloharawild
linkedin: mitchelloharawild
twitter: mitchoharawild
headcolor: 414141
output: vitae::awesomecv
---

```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
knitr::opts_chunk$set(echo = FALSE)
```

# Education
```{r}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
  "BCom (Hons) in Econometrics", "Monash University", "Clayton, Australia", "Mar. 2017 - Nov. 2017", "Recipient of the Econometrics Honours Memorial Scholarship, Dean's Honour, Dean's Commendation, and best in class for 5 units.",
  "BCom (Hons) in Econometrics", "Monash University", "Clayton, Australia", "Mar. 2017 - Nov. 2017", "Honours research project was to develop a state space model for quickly forecasting time series with multiple seasonalities.",
  "BCom (Hons) in Econometrics", "Monash University", "Clayton, Australia", "Mar. 2017 - Nov. 2017", "Studied units include Bayesian and frequentist econometrics, advanced statistical modelling and computational science.",
  "BCom in Econometrics, BSc in Mathematical statistics and Computational Science", "Monash University", "Clayton, Australia", "Mar. 2013 - Nov. 2016", "Recipient of the Monash Community Leaders Scholarship, International Institute of Forecasters Award, and best in class for 4 units.",
  "BCom in Econometrics, BSc in Mathematical statistics and Computational Science", "Monash University", "Clayton, Australia", "Mar. 2013 - Nov. 2016", "Mentor for the Access Monash Ambassador Program (2015 and 2016)",
  "BCom in Econometrics, BSc in Mathematical statistics and Computational Science", "Monash University", "Clayton, Australia", "Mar. 2013 - Nov. 2016", "Participant of the Vice-Chancellor's Ancora Imparo Student Leadership Program (2014)",
  "BCom in Econometrics, BSc in Mathematical statistics and Computational Science", "Monash University", "Clayton, Australia", "Mar. 2013 - Nov. 2016", "Studied a broad collection of units covering many aspects of data science. The three disciplines I majored in explored different perspectives for working with data."
) %>% 
  detailed_entries(degree, dates, uni, loc, details)
```

# Data consulting experience

```{r}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Data scientist", "Nectric", "Clayton, Australia", "Jan. 2019 - Present", "A variety of consulting projects with substantial spatio-temporal modelling tasks.",
  "Research assistant", "Monash University", "Clayton, Australia", "Jan. 2016 - Present", "Involved in many internal and external data projects of varying size and complexity.",
  "Research assistant", "Monash University", "Clayton, Australia", "Jan. 2016 - Present", "Projects typically feature large scale time series modelling or analysis, cross-sectional modelling and creating tools for improving workflows.",
  "Research assistant", "Monash University", "Clayton, Australia", "Jan. 2016 - Present", "Consulting project clients include: Huawei, Monash University, R Consortium, NSW Chief Scientist office, DiabetesLab and Tennis Australia.",
  "Data mining intern", "iSelect", "Cheltenham, Australia", "Feb. 2015 - Mar. 2015", "Improved business reporting with interactive visualisations, and model-based anomaly detection.",
) %>% 
  detailed_entries(role, dates, company, loc, details)
```

# Teaching experience

## University

```{r}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Teaching Associate", "Monash University", "Caulfield & Clayton, Australia", "S1 2016 - Present", "Advanced statistical modelling (ETC3580)",
  "Teaching Associate", "Monash University", "Caulfield & Clayton, Australia", "S1 2016 - Present", "Business forecasting (ETF3231/ETF5231)",
  "Teaching Associate", "Monash University", "Caulfield & Clayton, Australia", "S1 2016 - Present", "Mathematics for business (ETF2700)",
  "Teaching Associate", "Monash University", "Caulfield & Clayton, Australia", "S1 2016 - Present", "Data modelling and computing (ETC1010)"
) %>% 
  detailed_entries(role, dates, company, loc, details)
```

Purple letters (ETF5231 S1 2018, ETC3580 S2 2018, ETC3550 S1 2019)

## Workshops

fable rstudio::conf20
shiny CSIRO
fable WSC
data wrangling ESSA
gganimate NUMBAT
https://blog.rstudio.com/2016/10/28/join-hadley-wickhams-master-r-workshop-in-melbourne-australia-december-12-13/

# Software development

fable
forecast
icon
vitae
tsibbledata
tsfeatures
feasts
fabletools
fable.prophet
fasster
taipan
tsibble

tidyverse developer day

# Research experience

## Academic contributions

fasster, taipan, fable

sugarbag

## Presentations

https://www.meetup.com/en-AU/MelbURN-Melbourne-Users-of-R-Network/events/242402188/
https://www.meetup.com/en-AU/Timeseries-Forecasting-and-Event-Analytics-Melbourne-Meetup/events/255450499/
useR! 2018
useR! 2019
ISF19

<!-- # Relevant Skills -->
<!-- ```{r} -->
<!-- cvskill("Data Analysis", c("Visualisation", "Data Cleaning", "Forecasting", "Modelling", "Communication", "Inference", "Machine Learning", "Web Scraping")) -->
<!-- cvskill("Programming", c("R", "Python", "SQL", "Java", "C", "C++", "HTML/CSS", "TeX", "MATLAB")) -->
<!-- ``` -->

<!-- # Awards & Achievements -->
<!-- ## Awards -->
<!-- ```{r} -->
<!-- tribble( -->
<!--   ~ award, ~ from, ~ year, -->
<!--   "Commerce Dean's Honour", "Monash", "2017", -->
<!--   "Commerce Dean's Commendation", "Monash", "2016", -->
<!--   "Science Dean’s List", "Monash", "2014-2016", -->
<!--   "International Institute of Forecasters Award", "IIF", "2014", -->
<!--   "Rotary Youth Leadership Award", "Rotary", "2013" -->
<!-- ) %>% -->
<!--   brief_entries(award, year, from) -->
<!-- ``` -->

<!-- ## Scholarships -->
<!-- ```{r} -->
<!-- tribble( -->
<!--   ~ scholarship, ~ from, ~ year, -->
<!--   "Econometrics Honours Memorial Scholarship", "Monash", "2017", -->
<!--   "Monash Community Leaders Scholarship", "Monash", "2015 & 2016", -->
<!--   "Mitcham Rotary Scholarship", "Rotary", "2011 & 2012" -->
<!-- ) %>% -->
<!--   brief_entries(scholarship, year, from) -->
<!-- ``` -->

<!-- \hspace{3em} -->

<!-- ## Competitions -->
<!-- ```{r} -->
<!-- tribble( -->
<!--   ~ competition, ~ from, ~ year, -->
<!--   "UseR! 2018 Datathon Champion", "UseR!", "2018", -->
<!--   "RMIT SBITL Analytics Competition Champion", "RMIT", "2017", -->
<!--   "RMIT SBITL Analytics Competition Champion", "RMIT", "2016" -->
<!-- ) %>% -->
<!--   brief_entries(competition, year, from) -->
<!-- ``` -->
