---
name: Mitchell O'Hara-Wild
date: "`r format(Sys.time(), '%B, %Y')`"
qualifications: BCom(Hons), BSc
position: Data Scientist
address: Melbourne, Australia
email: mail@mitchelloharawild.com
website: mitchelloharawild.com
github: mitchelloharawild
linkedin: mitchelloharawild
twitter: mitchoharawild
headcolor: "414141"
output: 
  vitae::awesomecv:
    keep_tex: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
knitr::opts_chunk$set(echo = FALSE)
```

# Current employment

```{r consulting}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Data science consultant", "Nectric", "Melbourne, Australia", "Jan. 2019 - Present", 
    list("Data science consulting projects including spatio-temporal modelling, and large scale forecasting.",
         "Hosting workshops improving data literacy, development, analysis and modelling capabilities."
    ),
  "Research assistant", "Monash University", "Clayton, Australia", "Oct. 2015 - Present", 
    list("Involved in many internal and external data projects of varying size and complexity.", 
         "Projects typically feature large scale time series modelling or analysis, cross-sectional modelling and creating tools for improving workflows.",
         "Consulting project clients include: COVID-19 Doherty Institute, Huawei, Monash University, R Consortium, and the NSW Chief Scientist office.",
         "Developer for The R Journal, producing software for managing submitted articles and publishing them in both interactive HTML and static PDF."),
  "Teaching Associate", "Monash University", "Clayton, Australia", "Mar. 2016 - Present", "Sessional teaching of university students undertaking Bachelor's and Master's degrees."
  # "Data mining intern", "iSelect", "Cheltenham, Australia", "Feb. 2015 - Mar. 2015", "Improved business reporting with interactive visualisations, and model-based anomaly detection.",
) %>% 
  detailed_entries(role, dates, company, loc, details)
```

# Education

```{r education}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
  "PhD in Econometrics", "Monash University", "Clayton, Australia", "Feb. 2023 - Present", 
    list("Recipient of the Monash Graduate Excellence Scholarship.",
         "Research in forecast reconciliation and the design of statistical software for forecasting."),
  "BCom (Hons) in Econometrics", "Monash University", "Clayton, Australia", "Mar. 2017 - Nov. 2017", 
    list("Recipient of the Econometrics Honours Memorial Scholarship, Dean's Honour, Dean's Commendation, and best in class for 5 units.",
         "Honours research project was to develop a state space model for quickly forecasting time series with multiple seasonalities.",
         "Studied units include Bayesian and frequentist econometrics, advanced statistical modelling and computational science."),
  "BCom in Econometrics, BSc in Mathematical statistics and Computational Science", "Monash University", "Clayton, Australia", "Mar. 2013 - Nov. 2016", 
    list("Recipient of the Monash Community Leaders Scholarship, International Institute of Forecasters Award, and best in class for 4 units.",
         "Mentor for the Access Monash Ambassador Program (2015 and 2016)",
         "Participant of the Vice-Chancellor's Ancora Imparo Student Leadership Program (2014)",
         "Studied a broad range of units covering many aspects of data science. The three disciplines I majored in explored different perspectives for working with data.")
) %>% 
  detailed_entries(degree, dates, uni, loc, details)
```

# Teaching experience

## University Tutoring

\begin{cvparagraph}
My teaching quality at Monash University has been consistently recognised with positive student evaluations and individual praise from my students. I generally teach applied forecasting and data analysis skills that give students a practical toolkit for working with data in industry. I have also been awarded nine congratulatory letters for outstanding student evaluations which indicates that the unit's teaching is among the best in the university.
\end{cvparagraph}
<!-- ```{r tutoring} -->
<!-- tribble( -->
<!--   ~ title, ~ code, ~ campus, ~ semester, ~ purple, -->
<!--   "Advanced R Programming", "ETC4500/ETC5450", "Clayton", "2024 S1", TRUE, -->
<!--   "Applied forecasting", "ETC3550/ETC5550", "Clayton", "2024 S1", TRUE, -->
<!--   "Applied forecasting", "ETC3550/ETC5550", "Clayton", "2023 S1", TRUE, -->
<!--   "Applied forecasting", "ETC3550/ETC5550", "Clayton", "2022 S1", TRUE, -->
<!--   "Communicating with Data", "ETC5523", "Clayton", "2021 S2", FALSE, -->
<!--   "Applied forecasting", "ETC3550/ETC5550", "Clayton", "2021 S1", TRUE, -->
<!--   "Communicating with Data", "ETC5523", "Clayton", "2020 S2", TRUE, -->
<!--   "Applied forecasting", "ETC3550/ETC5550", "Clayton", "2020 S1", TRUE, -->
<!--   "Advanced statistical modelling", "ETC3580", "Clayton", "2019 S2", TRUE, -->
<!--   "Data modelling and computing", "ETC1010", "Clayton", "2019 S2", FALSE, -->
<!--   "Data modelling and computing", "ETC1010", "Clayton", "2019 S1", FALSE, -->
<!--   "Applied forecasting for business and economics", "ETC3550/ETC5550", "Clayton", "2019 S1", TRUE, -->
<!--   "Data modelling and computing", "ETC1010", "Clayton", "2018 S2", FALSE, -->
<!--   "Advanced statistical modelling", "ETC3580", "Clayton", "2018 S2", TRUE, -->
<!--   "Business forecasting", "ETF3231/ETF5231", "Caulfield", "2018 S1", TRUE, -->
<!--   "Data modelling and computing", "ETC1010", "Clayton", "2017 S2", FALSE, -->
<!--   "Business forecasting", "ETF3231/ETF5231", "Caulfield", "2017 S1", FALSE, -->
<!--   "Mathematics for business", "ETF2700", "Caulfield", "2016 S2", FALSE, -->
<!--   "Business forecasting", "ETF3231/ETF5231", "Caulfield", "2016 S1", FALSE -->
<!-- ) %>%  -->
<!--   brief_entries(glue::glue("\\textbf{<code>}: <title> (Monash <campus>)", .open = "<", .close = ">"), semester, .protect = FALSE) -->
<!-- ``` -->

\newpage

## Workshops and trainings

\begin{cvparagraph}
In addition to sessional tutoring, I also teach data analysis workshops for industry professionals.
\end{cvparagraph}

```{r workshops}
tribble(
  ~ role, ~ course, ~ organisation, ~ country, ~ dates, ~ details,
  # "Instructor", "Tidy time series analysis and forecasting", "useR!", "Austria", "Jul.  2024", "Quick-start workshop for tidy forecasting in R",
  # "Instructor", "Tidy time series analysis and forecasting", "R/Medicine", "Online", "Jun. 2024", "Quick-start workshop for tidy forecasting in R",
  "Instructor", "Interactive web applications with Shiny for R", "SSA", "Online", "Dec. 2023", "Booked out 3-hour online quick-start workshop for the basics of shiny",
  "Instructor", "AFRICAST: Tidy forecasting for social good", "F4SG", "Online", "Oct. 2023", "Five day workshop on forecasting for 62 students from 9 Sub-Saharan African countries.",
  "Instructor", "Tidy Time Series and Forecasting in R", "NYR", "USA", "Jul. 2023", "Two day workshop on forecasting using tidy forecasting tools in R.",
  "Instructor", "Interactive web applications with Shiny", "WOMBAT", "Australia", "Dec. 2022", "Half-day workshop on the basics of shiny applications.",
  "Teaching assistant", "Tidy Time Series and Forecasting in R", "rstudio::conf", "USA", "Jan. 2020", "Two day workshop with Rob Hyndman on forecasting using tidyverse workflows.",
  "Instructor", "Interactive documents with Shiny", "CSIRO", "Australia", "Nov. 2019", "Two day intermediate workshop on developing of shiny applications.",
  "Instructor", "Data Wrangling", "Monash University", "Australia", "Sep. 2019", "A short workshop in the 'R Workshops for Beginners' series on using tidyr and dplyr to wrangle data.",
  "Helper", "Tidyverse developer day", "RStudio", "France", "Jul. 2019", "A one day developer day where I helped R users resolve issues on tidyverse packages.",
  "Teaching assistant", "High-dimensional time series analysis", "ISI WSC", "Malaysia", "Aug. 2019", "One day short course with Rob Hyndman for analysing and forecasting large collections of time series.",
  # "Instructor", "The grammar of animation", "Monash University", "Australia", "Mar. 2019", "A short workshop for NUMBAT group on creating animated graphics in R with the gganimate package.",
  # "Teaching assistant", "Master R Developer Workshop", "RStudio", "Australia", "Dec. 2016", "A two day workshop with Hadley Wicham on programming with R and developing R packages.",
) %>% 
  brief_entries(glue::glue("\\textbf{<course>}: <role> (<organisation>, <country>) \\newline <details>", .open = "<", .close = ">"), paste0(dates, "\\newline"), .protect = FALSE)
```


# Research output
## Software

\begin{cvparagraph}
My primary research output is the translation of academic research into open source software packages. In total I have been the lead developer or a substantial contributor to more than 20 open source R packages, many of which provide tools for analysing time series data and visualisations. This software has a significant impact to the industry, with the total average unique monthly downloads exceeding 100,000.
\end{cvparagraph}

```{r r-pkgs, include = FALSE}
tribble(
  ~ pkg, ~ when, ~ role, ~ details,
  "gghdr", "2022", "Author", "Extends ggplot2 with plot types for visualising highest density regions.",
  "distributional", "2020", "Lead developer", "Vectorised distribution objects with methods for manipulating and computing on probability distributions.",
  "fable", "2019", "Lead developer", "A collection of time series models for use in a tidyverse workflow.",
  "fable.prophet", "2019", "Lead developer", "Extension package implementing the prophet forecasting procedure for fable.",
  "feasts", "2019", "Lead developer", "A collection of features, decompositions, statistics and graphics tools for the analysing tidy time series data.",
  "fabletools", "2019", "Lead developer", "Provides common utilities for the fable forecasting framework, allows users to extend fable with new models.",
  "tsibbledata", "2019", "Lead developer", "Diverse datasets in a tidy time series data structure (tsibble). Useful in examples of tidy time series analysis.",
  "tsfeatures", "2019", "Author", "Various methods for extracting features from time series data.",
  "tsibble", "2018", "Contributor", "Tidy temporal data structures and tools. The data for the tidy time series collection of packages.",
  "vitae", "2018", "Lead developer", "Dynamically generate a Résumé or CV using R Markdown. This CV is created using code with that package!",
  "cransays", "2018", "Author", "Provides a dashboard and historical data for R packages being reviewed by CRAN.",
  "fasster", "2017", "Lead developer", "Implementation of the FASSTER model for forecasting complex multiple seasonal patterns.",
  "icons", "2017", "Lead developer", "Embed SVG icons in R documents such as slides, reports and apps.",
  "taipan", "2018", "Lead developer", "Generates shiny apps for annotating image data, which is useful for training machine learning models.",
  "ggquiver", "2017", "Lead developer", "Extends ggplot2 for displaying vector fields on plots.",
  "forecast", "2015", "Author", "Methods and tools analysing univariate time series data and producing model-based forecasts."
) %>% 
  brief_entries(glue::glue("\\textbf{<pkg>}: <role> \\newline <details>", .open = "<", .close = ">"), paste0(when, "\\newline"), .protect = FALSE)
```

<!-- ## Academic research -->

<!-- fasster, taipan, fable -->

## Presentations

```{r talks}
tribble(
  ~ when, ~ title, ~ details, ~ where, ~ url,
  "2023", "Creating flexible e-learning quizzes with literate programming", "Using literate programming to create Moodle quizzes", "NYR", "https://slides.mitchelloharawild.com/moodlequiz/",
  "2023", "From forecast to fable, design decisions for statistical software", "A comparison of the design differences between forecast and fable.", "NYR", "https://slides.mitchelloharawild.com/nyr2023/",
  "2023", "Reconciliation of structured time series forecasts with graphs", "Reconciling forecasts with graph constraints.", "ISF", "https://slides.mitchelloharawild.com/reconciling-graphs/",
  "2023", "The design of statistical software", "Discussion about design principles of user interfaces for statistics.", "NUMBAT Seminar", "https://slides.mitchelloharawild.com/statistical-software-design/",
  "2020", "Forecasting with multiple seasonality", "Methods and techniques to multiple seasonal forecasting in R", "UK NHS", "https://slides.mitchelloharawild.com/nhs2020/",
  "2020", "Probabilistic cross-temporal hierarchies", "Recent developments of temporal reconciliation in fable.", "ISF", "https://slides.mitchelloharawild.com/isf2020/",
  "2019", "Flexible futures for fable functionality", "Gradual introduction to tidy forecasting with fable. Flexibility is demonstrated with combination modelling and package extensibilitiy.", "MelbURN meetup", "https://slides.mitchelloharawild.com/fable-tfeam/",
  "2019", "Flexible futures for fable functionality", "Reconciled forecasting of many time series with model combinations.", "ISF", "https://slides.mitchelloharawild.com/isf2019/",
  "2018", "Tidy forecasting in R", "Discussion of recent developments to the fable framework.", "MelbURN meetup", "https://slides.mitchelloharawild.com/fable-tfeam/",
  "2018", "Forecasting multiple seasonality with state switching", "The FASSTER model with the fable framework.", "useR!", "https://slides.mitchelloharawild.com/user2018",
  "2017", "Models for forecasting multiple seasonality", "An introduction to the FASSTER model.", "MelbURN meetup", "https://slides.mitchelloharawild.com/melburn17/",
) %>% 
  brief_entries(glue::glue("\\textbf{<title>}: <details> \\newline \\url{<url>}", .open = "<", .close = ">"), when, .protect = FALSE)
```

## Publications

```{r}
bibliography_entries("publications.bib")
```

<!-- # Data analysis projects -->

<!-- # Related interests -->
<!-- * Home automation -->
<!-- * Beekeeping -->
<!-- * Permaculture -->
<!-- * Electronics design -->
<!-- * Woodworking -->

<!-- # Relevant Skills -->
<!-- ```{r} -->
<!-- cvskill("Data Analysis", c("Visualisation", "Data Cleaning", "Forecasting", "Modelling", "Communication", "Inference", "Machine Learning", "Web Scraping")) -->
<!-- cvskill("Programming", c("R", "Python", "SQL", "Java", "C", "C++", "HTML/CSS", "TeX", "MATLAB")) -->
<!-- ``` -->

# Awards & Achievements
## Awards
```{r}
tribble(
  ~ award, ~ from, ~ year,
  "Student Presentation Award", "ISF", "2023",
  "Dean's Citation for Outstanding Contribution to Student Learning as a Teaching Associate", "Monash", "2021",
  "Commerce Dean's Honour", "Monash", "2017",
  "Commerce Dean's Commendation", "Monash", "2016",
  "Science Dean’s List", "Monash", "2014-2016",
  "International Institute of Forecasters Award", "IIF", "2014",
  "Rotary Youth Leadership Award", "Rotary", "2013"
) %>%
  brief_entries(award, year, from)
```

## Scholarships
```{r}
tribble(
  ~ scholarship, ~ from, ~ year,
  "Monash Graduate Excellence Scholarship", "Monash", "2023 - 2026",
  "Monash Faculty Scholarship", "Monash", "2023 - 2026",
  "Monash Departmental Scholarship", "Monash", "2023 - 2026",
  "Econometrics Honours Memorial Scholarship", "Monash", "2017",
  "Monash Community Leaders Scholarship", "Monash", "2015 & 2016",
  "Mitcham Rotary Scholarship", "Rotary", "2011 & 2012"
) %>%
  brief_entries(scholarship, year, from)
```

<!-- ## Competitions -->
<!-- ```{r} -->
<!-- tribble( -->
<!--   ~ competition, ~ from, ~ year, -->
<!--   "UseR! 2018 Datathon Champion", "UseR!", "2018", -->
<!--   "RMIT SBITL Analytics Competition Champion", "RMIT", "2017", -->
<!--   "RMIT SBITL Analytics Competition Champion", "RMIT", "2016" -->
<!-- ) %>% -->
<!--   brief_entries(competition, year, from) -->
<!-- ``` -->
